Run the model

### 2022-05-28 scripts/3_model/2_run_model.Rmd
Updating for dissertation

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Losses\n(relative to R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

```{r}
ggsave(plot = costs_no_trading_plot,
       filename = here("docs", "slides", "img", "cost_no_trading.png"),
       width = 3,
       height = 3)
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses (relative to R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot_long_axis,
       filename = here("docs", "slides", "img", "cost_with_trading_long_axis.png"),
       width = 3,
       height = 3)
```

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses\n(relative to R = 0)") +
  scale_color_viridis_c() +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot,
       filename = here("docs", "slides", "img", "cost_with_trading.png"),
       width = 3,
       height = 3)
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0.885, 1)) +
  scale_x_continuous(limi= c(0, 1)) +
  theme(legend.position = "None"))

ggsave(plot = delta_costs_plot,
       filename = here("docs", "img", "panel2c.pdf"),
       width = 3.4, height = 2.3)
```

@@

```{r}
ggsave(plot = cost_plot,
       filename = here("docs", "img", "PNA_model.pdf"),
       width = 3.4,
       height = 7)
```

@@

```{r}
ggsave(plot = effort_and_revenues,
       file = here("docs", "img","effort_and_revenues.pdf"),
       width = 6,
       height = 4)
```

```{r}
ggsave(plot = effort_and_revenues,
       file = here("docs", "img","effort_and_revenues_ED_Fig4.tiff"),
       width = 6,
       height = 4)
```

@@

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       filename = here("docs", "img", "vessel_day_price_no_trading_plot.pdf"),
       width = 6,
       height = 3)
```

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       filename = here("docs", "img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
       width = 6,
       height = 3)
```

@@

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       filename = here("docs", "img", "vessel_day_price_with_trading_plot.pdf"),
       width = 6,
       height = 4.5)
```

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       filename = here("docs", "img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
       width = 6,
       height = 4.5)
```

@@

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot.pdf"),
       width = 3,
       height = 3)
```

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       filename = here("docs", "img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
       width = 3,
       height = 3)
```

@@

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3.5
)
```

```{r}
#Slide export
ggsave(
  plot = allocation_cost_plot,
  filename = here("docs", "slides", "img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3
)
```

>>>>

```{r, fig.width = 4, fig.height = 4}
(
  costs_no_trading_plot <-
    ggplot(data = DF_1_no_trading) +
    geom_line(aes(
      x = R,
      y = rel_cost,
      group = theta,
      color = theta
    ),
    size = 1
    ) +
    xlab("Portion of patch as reserve (R)") +
    ylab("Losses\n(relative to R = 0)") +
    scale_color_viridis_c() +
    theme(
      text = element_text(size = 10),
      axis.text = element_text(size = 8)
    ) +
    # startR::ggtheme_plot() +
    scale_y_continuous(labels = scales::percent) +
    guides(color = guide_colorbar(title = quo("Movement ("~theta~")"),
                                  ticks.colour = "black", frame.colour = "black")) +
    theme(legend.justification = c(0, 0.9),
          legend.position = c(0, 1)) +
    geom_abline(intercept = 0, slope = 1, size = 1, linetype = "dashed", color = "red")
)
```

```{r}
ggsave(plot = costs_no_trading_plot,
       filename = here("docs", "diss_img", "cost_no_trading.png"),
       width = 3,
       height = 3)
```

@@

```{r, fig.width = 4, fig.height = 4}
(costs_with_trading_plot_long_axis <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses (relative to R = 0)") +
  scale_color_viridis_c() +
  # startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent, limits = c(0, 1)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot_long_axis,
       filename = here("docs", "diss_img", "cost_with_trading_long_axis.png"),
       width = 3,
       height = 3)
```

```{r}
(costs_with_trading_plot <- ggplot(data = DF_1_with_trading) +
  geom_line(aes(
    x = R,
    y = rel_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Losses\n(relative to R = 0)") +
  scale_color_viridis_c() +
  # startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.01)) +
  theme(legend.position = "None"))
```

```{r}
ggsave(plot = costs_with_trading_plot,
       filename = here("docs", "diss_img", "cost_with_trading.png"),
       width = 3,
       height = 3)
```

@@

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  # startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0.885, 1)) +
  scale_x_continuous(limi= c(0, 1)) +
  theme(legend.position = "None"))

ggsave(plot = delta_costs_plot,
       filename = here("docs", "diss_img", "panel2c.pdf"),
       width = 3.4, height = 2.3)
```

@@

```{r}
ggsave(plot = cost_plot,
       filename = here("docs", "diss_img", "PNA_model.pdf"),
       width = 3.4,
       height = 7)
```

@@

```{r}
ggsave(plot = effort_and_revenues,
       file = here("docs", "diss_img", "effort_and_revenues.pdf"),
       width = 6,
       height = 4)
```

```{r}
ggsave(plot = effort_and_revenues,
       here("docs", "diss_img", "effort_and_revenues_ED_Fig4.tiff"),
       width = 6,
       height = 4)
```

@@

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       filename = here("docs", "diss_img", "vessel_day_price_no_trading_plot.pdf"),
       width = 6,
       height = 3)
```

```{r}
ggsave(plot = vessel_day_price_no_trading_plot,
       here("docs", "diss_img", "vessel_day_price_no_trading_plot_ED_Fig1.tiff"),
       width = 6,
       height = 3)
```

@@

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       here("docs", "diss_img", "vessel_day_price_with_trading_plot.pdf"),
       width = 6,
       height = 4.5)
```

```{r}
ggsave(plot = vessel_day_price_with_trading_plot,
       here("docs", "diss_img", "vessel_day_price_with_trading_plot_ED_Fig3.tiff"),
       width = 6,
       height = 4.5)
```

@@

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       here("docs", "diss_img", "profits_PNA_notKIR_no_trading_plot.pdf"),
       width = 3,
       height = 3)
```

```{r}
ggsave(plot = profits_PNA_notKIR_no_trading_plot,
       here("docs", "diss_img", "profits_PNA_notKIR_no_trading_plot_ED_Fig2.tiff"),
       width = 3,
       height = 3)
```

@@

```{r}
#Paper export
ggsave(
  plot = allocation_cost_plot,
  here("docs", "diss_img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3.5
)
```

```{r}
#Slide export
ggsave(
  plot = allocation_cost_plot,
  here("docs", "diss_img", "allocation_cost_plot.pdf"),
  width = 5,
  height = 3
)
```
